Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-12-16 latex/ms.tex
add derivation of pi_PO in appendix, #8

In the main text, we ignore the variation of reproductive potential among parents (i.e., both $\lambda_{i,1}$ and $\lambda_{j,2}$ are constant) to derive $\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$, which corresponds to the probability that two offspring sampled in the population 1 and 2 share an HS relationship and that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship, respectively. Let $k_{i,1}$ and $k_{j,2}$ be the number of surviving offspring of parent $i$ and $j$ at sampling in the population 1 and 2, respectively, and $k_{i,1}$ and $k_{j,2}$ is assumed to follow a kind of discrete distribution (e.g., negative binomial distribution) with mean $\lambda_{i,1}$ and $\lambda_{j,2}$. Without loss of generality, we set the index such that parents with $i=1$ to $M$ in the population 1 and $j=1$ to $M$ in the population 2 are identical migrants; for example, the parent with $i=1$ reproduce $k_{1,1}$ offspring (in the population 1) and then reproduce $k_{1,2}$ offspring (in the population 2) after migration. Giving $k_{i,1}$ and $k_{j,2}$, the conditional probability that two offspring sampled in the population 1 and 2 share an HS relationship is

@@

>>>>

In the main text, we ignore the variation of reproductive potential among parents (i.e., both $\lambda_{i,1}$ and $\lambda_{j,2}$ are constant) to derive $\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$. Let $k_{i,1}$ and $k_{j,2}$ be the number of surviving offspring of parent $i$ and $j$ at sampling in the population 1 and 2, respectively, and $k_{i,1}$ and $k_{j,2}$ is assumed to follow a kind of discrete distribution (e.g., negative binomial distribution) with mean $\lambda_{i,1}$ and $\lambda_{j,2}$. Without loss of generality, we set the index such that parents with $i=1$ to $M$ in the population 1 and $j=1$ to $M$ in the population 2 are identical migrants; for example, the parent with $i=1$ reproduce $k_{1,1}$ offspring (in the population 1) and then reproduce $k_{1,2}$ offspring (in the population 2) after migration. Giving $k_{i,1}$ and $k_{j,2}$, the conditional probability that two offspring sampled in the population 1 and 2 share an HS relationship is

@@

Similar to the derivation of $\pi_{\rm HS,bet}$, the conditional probability that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship is
\begin{align}
\pi_{\rm PO,bet} | _{\boldsymbol{k_1, k_2}} &= \frac{ 2\sum_{i=1}^M k_{i,1} } { \sum_{i=1}^{N_1} k_{i,1} } \frac{ \sum_{j=1}^M k_{j,2} } { \sum_{j=1}^{N_2} k_{j,2} } \frac{1}{M}.
\end{align}
By taking the expectation over $k$ and $\lambda$, in the same manner as noted above, the unconditional probability is given by
\begin{align}
\pi_{\rm PO,bet} &= \mathbb{E}[\mathbb{E}[\pi | _{\boldsymbol{k_1, k_2}}]] \nonumber\\ 
&\approx  \frac{2M}{N_{1}N_{2}},
\end{align}
which provides the same formulation described in Eq.\ref{PO-1}.

\section*{APPENDIX 3}
